### 2020-08-21 spanish/sections/awards.tex
Create awards.tex

\cvsection{Honours \& Awards}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College at the University of Oxford Book and Travel Grants} 
{Allowances for books and conference participation (travel grant was declined because of coronavirus pandemic), {\pounds} 745} 
{Oxford, UK}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Becas Chile Doctoral Scholarship Abroad} 
{Tuition fees, transport and living expenses for pursuing a DPhil at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160,000}
{Oxford, UK}
{2019}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{LASA Travel Grant} 
{Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
{New York, USA}
{2016}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{CESS Summer School Scholarship}
{Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
{Santiago, Chile}
{2016}
\end{cvhonors}

>>>>

\cvsection{Honores y premios}

@@

\begin{cvhonors}
\cvhonor
{Becas de Libros y Viaje St Hilda's College en la Universidad de Oxford} 
{Asignaciones para libros y participación en conferencias (la subvención para viajes se rechazó debido a la pandemia de coronavirus), USD{\$} 970} 
{Oxford, RU}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Becas Chile, Beca Doctorado en el Extranjero } 
{Tasas de matrícula, transporte y gastos de manutención para obtener un doctorado en la Universidad de Oxford (ANID/PFCHA/72200340), USD{\$} 210.000}
{Oxford, RU}
{2019}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Beca de Viaje LASA} 
{Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
{Nueva York, EUA}
{2016}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Beca CESS Escuela de Verano}
{Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
{Santiago, Chile}
{2016}
\end{cvhonors}
